---
title: "Algeria"
output: html_document
date: "2024-11-18"
---

```{r, warning=F, echo=F, message=F}
source("Functions.R")
country="Algeria"
management_fcn()
```

Algeria is a North African country of 46.3 million people with a coastline along the Mediterranean sea. A former French colony, the modern country of Algeria gained it's independence after a long and costly war in 1962. It's navy dates back from its independence and the country stayed non-aligned throughout the cold war, allowing it to source material from a variety of countries. Its major surface fleet units today include an Italian built amphibious transport dock, 2 British built landing ships, and 9 frigates or large corvettes (2 German, 4 Chinese, and 3 Soviet built).

Algeria is a relatively new entry in the world of submarines. All acquisitions in this domain have come from Soviet and Russian sources. A total of 8 submarines have operated in the Algerian navy. The two initial second-hand Romeo class (Project 633), served briefly before being replaced by 2 newly built Kilo class (Project 877) in the late 1980s. These have since been complemented by 4 improved Kilo class (Project 636) in the 21st century. All 6 Kilo class submarines are still active today.

# Submarines operated by Algeria

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=5}
summary_fcn()
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=7}
weapons_fcn()
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=5}
class_fcn()
```

# Individual submarines by class

## Specification summaries

```{r, warning=F, echo=F, message=F, fig.width=13, fig.height=4/4+1}
specs1_fcn()
```

```{r, warning=F, echo=F, message=F, fig.width=13, fig.height=4/2+2}
specs2_fcn()
```

## Romeo class (Project 633)

The first Algerian submarines were second-hand Soviet Romeo class which had a short career. They were more training boats then anything else until the arrival of the new Kilo boats.

```{r, warning=F, echo=F, message=F}
kable(specs[specs$Class=="Project 633",c("Version","Boats","Number","Displacement","Propulsion","Power","Fuel","Speed","Range","Depth")])
kable(weaps[weaps$Class=="Project 633",c("Version","Boats","Year","Torpedo_text")])
```

![](https://www.shipbucket.com/files/real/DZ/Project%20633%20(Romeo)/none/9235_010_20230511193114.png)

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=4}
class_serv_fcn(class="Project 633")
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=2/4+1}
class_sub_fcn(class="Project 633")
```

## Kilo class (Projects 877 and 636)

Algeria's current submarine force consists of 3 pairs of Kilo class submarines acquired new from the Soviet Union, and then Russia over several decades.

```{r, warning=F, echo=F, message=F}
kable(specs[specs$Class=="Project 877",c("Version","Boats","Number","Displacement","Propulsion","Power","Fuel","Speed","Range","Depth")])
kable(weaps[weaps$Class=="Project 877",c("Version","Boats","Year","Torpedo_text","Missile_text","Light_SAM")])
```

![](https://www.shipbucket.com/files/real/DZ/Project%20636M%20Varshavyanka%20(Improved%20Kilo)/none/9077_021MessalielHadj_20230511193118.png)

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=4}
class_serv_fcn(class="Project 877")
class_batch_fcn(class="Project 877")
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=6/4+1}
class_sub_fcn(class="Project 877")
```

# Full summary

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=(8/4+1)}
individual_fcn()
```
