---
title: "Algeria"
output: html_document
date: "2024-11-18"
---

```{r, warning=F, echo=F, message=F}
#Package loading

library(data.table)
library(ggplot2)
library(patchwork)
library(janitor) #to build markdown table (tabyl and adorn functions)
library(knitr) #to make table in html format (kable function)
library(dplyr) #to use the %<% sign
library(ggalluvial)
library(networkD3) # for flowchart
library(tidyverse) #for flowcharts
library(ggrepel) # for pie charts
library(reshape2)
library(directlabels)
#library(kableExtra)
```

```{r, warning=F, echo=F, message=F}
#Data loading
submarine0=readRDS("submarine.rds")
specs0=readRDS("specifics.rds")
weaps0=readRDS("weapons.rds")
```

```{r, warning=F, echo=F, message=F}
submarine=submarine0[(submarine0$Operator=="Algeria" | submarine0$Builder=="Algeria" | submarine0$Design=="Algeria") & submarine0$Fate!="cancelled" & submarine0$Fate!="ordered",]
specs=specs0[(specs0$Operator=="Algeria" | specs0$Design=="Algeria"),]
weaps=weaps0[(weaps0$Operator=="Algeria" | weaps0$Design=="Algeria"),]

Type_list = unique(submarine$Type)
Propulsion_list = unique(submarine$Propulsion)
Builder_list = unique(submarine$Builder)
Operator_list = unique(submarine$Operator)

Type_list_prod = unique(submarine[submarine$Builder=="Algeria",]$Type)
Propulsion_prod = unique(submarine[submarine$Builder=="Algeria",]$Propulsion)
Type_list_serv = unique(submarine[submarine$Operator=="Algeria",]$Type)
Propulsion_serv = unique(submarine[submarine$Operator=="Algeria",]$Propulsion)
Builder_list = unique(submarine[submarine$Operator=="Algeria",]$Builder)
Operator_list = unique(submarine[submarine$Builder=="Algeria",]$Operator)
Class_list_prod = unique(submarine[submarine$Builder=="Algeria",]$Class)
Class_list_prod1 = unique(submarine[submarine$Builder=="Algeria" & submarine$Laid<="1920-01-01",]$Class)
Class_list_prod2 = unique(submarine[submarine$Builder=="Algeria" & submarine$Compl>="1920-01-01" & submarine$Laid<="1950-01-01",]$Class)
Class_list_prod3 = unique(submarine[submarine$Builder=="Algeria" & submarine$Compl>="1950-01-01",]$Class)
Class_list_serv = unique(submarine[submarine$Operator=="Algeria",]$Class)
Class_list_serv1 = unique(submarine[submarine$Operator=="Algeria" & submarine$Comm<="1920-01-01",]$Class)
Class_list_serv2 = unique(submarine[submarine$Operator=="Algeria" & submarine$Decomm>="1920-01-01" & submarine$Comm<="1950-01-01",]$Class)
Class_list_serv3 = unique(submarine[submarine$Operator=="Algeria" & submarine$Decomm>="1950-01-01",]$Class)

Version_list_prod = unique(submarine[submarine$Builder=="Algeria",]$Version)
Version_list_prod1 = unique(submarine[submarine$Builder=="Algeria" & submarine$Laid<="1920-01-01",]$Version)
Version_list_prod2 = unique(submarine[submarine$Builder=="Algeria" & submarine$Compl>="1920-01-01" & submarine$Laid<="1950-01-01",]$Version)
Version_list_prod3 = unique(submarine[submarine$Builder=="Algeria" & submarine$Compl>="1950-01-01",]$Version)
Version_list_serv = unique(submarine[submarine$Operator=="Algeria",]$Version)
Version_list_serv1 = unique(submarine[submarine$Operator=="Algeria" & submarine$Comm<="1920-01-01",]$Version)
Version_list_serv2 = unique(submarine[submarine$Operator=="Algeria" & submarine$Decomm>="1920-01-01" & submarine$Comm<="1950-01-01",]$Version)
Version_list_serv3 = unique(submarine[submarine$Operator=="Algeria" & submarine$Decomm>="1950-01-01",]$Version)

Batch_list_prod = unique(submarine[submarine$Builder=="Algeria",]$Batch)
Batch_list_prod1 = unique(submarine[submarine$Builder=="Algeria" & submarine$Laid<="1920-01-01",]$Batch)
Batch_list_prod2 = unique(submarine[submarine$Builder=="Algeria" & submarine$Compl>="1920-01-01" & submarine$Laid<="1950-01-01",]$Batch)
Batch_list_prod3 = unique(submarine[submarine$Builder=="Algeria" & submarine$Compl>="1950-01-01",]$Batch)
Batch_list_serv = unique(submarine[submarine$Operator=="Algeria",]$Batch)
Batch_list_serv1 = unique(submarine[submarine$Operator=="Algeria" & submarine$Comm<="1920-01-01",]$Batch)
Batch_list_serv2 = unique(submarine[submarine$Operator=="Algeria" & submarine$Decomm>="1920-01-01" & submarine$Comm<="1950-01-01",]$Batch)
Batch_list_serv3 = unique(submarine[submarine$Operator=="Algeria" & submarine$Decomm>="1950-01-01",]$Batch)

weaps$Torpedo=paste0(weaps$Tubes,"x",weaps$Torp_type," (",weaps$Torpedoes," torp or ",weaps$Tube_mines, " mines)")

specs$Total=specs$Number + specs$Incomplete
specs$Submarines=paste0(specs$Batch,", ",specs$Boats,", ",specs$Year)
weaps$Submarines=paste0(weaps$Batch,", ",weaps$Boats,", ",weaps$Year)
specs$Displacement_t=paste0(specs$Disp_full_surf_t,"/", specs$Disp_full_sub_t)
specs$Power_HP=paste0(specs$Power_surf_HP,"/", specs$Power_sub_HP)
specs$Speed_kts=paste0(specs$Speed_surf_kts,"/", specs$Speed_sub_kts)
specs$Range_nm=paste0(specs$Range_surf_nm,"/", specs$Range_sub_nm)
```

Algeria is a North African country of 46.3 million people with a coastline along the Mediterranean sea. A former French colony, the modern country of Algeria gained it's independence after a long and costly war in 1962. It's navy dates back from its independence and the country stayed non-aligned throughout the cold war, allowing it to source material from a variety of countries. Its major surface fleet units today include an Italian built amphibious transport dock, 2 British built landing ships, and 9 frigates or large corvettes (2 German, 4 Chinese, and 3 Soviet built).

Algeria is a relatively new entry in the world of submarines. All acquisitions in this domain have come from Soviet and Russian sources. A total of 8 submarines have operated in the Algerian navy. The two initial second-hand Romeo class (Project 633), served briefly before being replaced by 2 newly built Kilo class (Project 877) in the late 1980s. These have since been complemented by 4 improved Kilo class (Project 636) in the 21st century. All 6 Kilo class submarines are still active today.

# Submarines operated by Algeria

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=5}
g21=ggplot(submarine[submarine$Status!="modernized" & submarine$Fate!="incomplete" & submarine$Operator=="Algeria",], aes(Comm.y)) + geom_bar(col="black", aes(fill=Status)) + scale_fill_manual(values=c(
     "new"="blue",
     "resumed"="lightblue3",
     "second-hand"="green3")) + ggtitle("operated submarine commissionings") + xlab("year") + ylab("number of submarines") + theme(legend.position="bottom")

g22=ggplot(submarine[submarine$Fate!="modernized" & submarine$Operator=="Algeria",], aes(Stricken.y)) + geom_bar(col="black", aes(fill=Fate)) + scale_fill_manual(values=c(
     "lost"="red",
     "total loss"="red",
     "scuttled"="purple",
     "transferred"="forestgreen",
     "transferred incomplete"="green3",
     "captured"="brown",
     "captured incomplete"="brown3",
     "surrendered"="lightblue",
     "transferred incomplete"="lightgreen",
     "retired"="lightcyan",
     "hulked"="lightcyan",
     "museum"="lightcyan",
     "incomplete"="lemonchiffon2",
     "cancelled"="lemonchiffon",
     "active"="darkblue",
     "building"="goldenrod1",
     "ordered"="lightgrey")) + ggtitle("operated submarine fates") + xlab("year") + ylab("number of submarines") + theme(legend.position="bottom", axis.title.x = element_blank(), axis.title.y = element_blank())
(g21+g22)
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=5}
Timeline_op=data.frame(day=seq(as.Date(min(submarine$Laid)-30), as.Date("2024-06-01"), by="month"))
Timeline_op$Incomplete=NA
Timeline_op$Retired=NA
Timeline_op$Ex_Captured=NA
Timeline_op$Captured=NA
Timeline_op$Ex_Transferred=NA
Timeline_op$Transferred=NA
Timeline_op$Scuttled=NA
Timeline_op$Lost=NA
Timeline_op$Reserve=NA
Timeline_op$Service=NA
Timeline_op$Transit=NA
Timeline_op$Construction=NA

for (i in 1:nrow(Timeline_op)) {
  Timeline_op$Incomplete[i]=sum(submarine[(submarine$Stricken<=Timeline_op$day[i] & submarine$Fate=="incomplete" & submarine$Operator=="Algeria"),]$value)
  Timeline_op$Retired[i]=sum(submarine[(submarine$Stricken<=Timeline_op$day[i] & submarine$Fate%in%c("hulked","museum","retired","surrendered") & submarine$Operator=="Algeria"),]$value)
  Timeline_op$Captured[i]=sum(submarine[(submarine$Stricken<=Timeline_op$day[i] & submarine$Foreign>Timeline_op$day[i] & submarine$Fate%in%c("captured","captured incomplete") & submarine$Operator=="Algeria"),]$value)
  Timeline_op$Ex_Captured[i]=sum(submarine[(submarine$Foreign<=Timeline_op$day[i] & submarine$Fate%in%c("captured","captured incomplete") & submarine$Operator=="Algeria"),]$value)
  Timeline_op$Transferred[i]=sum(submarine[(submarine$Stricken<=Timeline_op$day[i] & submarine$Foreign>Timeline_op$day[i] & submarine$Fate%in%c("transferred","transferred incomplete") & submarine$Operator=="Algeria"),]$value)
  Timeline_op$Ex_Transferred[i]=sum(submarine[(submarine$Foreign<=Timeline_op$day[i] & submarine$Fate%in%c("transferred","transferred incomplete") & submarine$Operator=="Algeria"),]$value)
  Timeline_op$Scuttled[i]=sum(submarine[(submarine$Stricken<=Timeline_op$day[i] & submarine$Fate=="scuttled" & submarine$Operator=="Algeria"),]$value)
  Timeline_op$Lost[i]=sum(submarine[(submarine$Stricken<=Timeline_op$day[i] & submarine$Fate%in%c("lost","total loss") & submarine$Operator=="Algeria"),]$value)
  Timeline_op$Reserve[i]=sum(submarine[(submarine$Decomm<=Timeline_op$day[i] & submarine$Stricken>Timeline_op$day[i] & submarine$Operator=="Algeria"),]$value)
  Timeline_op$Service[i]=sum(submarine[(submarine$Comm<=Timeline_op$day[i] & submarine$Decomm>Timeline_op$day[i] & submarine$Operator=="Algeria"),]$value)
  Timeline_op$Transit[i]=sum(submarine[(submarine$Compl<=Timeline_op$day[i] & submarine$Comm>Timeline_op$day[i] & submarine$Status=="new" & submarine$Operator=="Algeria"),]$value)
  Timeline_op$Construction[i]=sum(submarine[(submarine$Laid<=Timeline_op$day[i] & submarine$Compl>Timeline_op$day[i] & submarine$Status=="new" & submarine$Operator=="Algeria"),]$value)
}

Timeline_op2=melt(Timeline_op, id.vars=c("day"),variable.name = "Status")

g24=ggplot(Timeline_op2, aes(day,value)) + geom_area(aes(fill=Status), col="black") + scale_fill_manual(values=c(
     "Incomplete"="lemonchiffon",
     "Retired"="lightgrey",
     "Transferred"="forestgreen",
     "Ex_Transferred"="lightgreen",
     "Captured"="brown",
     "Ex_Captured"="lightsalmon",
     "Scuttled"="purple",
     "Lost"="red",
     "Reserve"="lightblue",
     "Service"="darkblue",
     "Transit"="lightblue",
     "Construction"="goldenrod1")) + ggtitle("Algerian operated submarines") + xlab("date") + ylab("number of submarines") + theme(legend.position="bottom")


print(g24)
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=7}
Timeline_wep=data.frame(day=seq(as.Date(min(submarine$Laid)-30), as.Date(max(submarine$Stricken)+30), by="month"))
Timeline_wep$Mine=NA
Timeline_wep$SLBM=NA
Timeline_wep$VLS=NA
Timeline_wep$Torpedoes=NA
Timeline_wep$Torpedo_tubes=NA


for (i in 1:nrow(Timeline_wep)) {
  Timeline_wep$Service[i]=sum(submarine[(submarine$Comm<=Timeline_wep$day[i] & submarine$Stricken>Timeline_wep$day[i] & submarine$Operator=="Algeria"),]$value)
  Timeline_wep$Torpedo_tubes[i]=sum(submarine[(submarine$Operator=="Algeria" & submarine$Comm<=Timeline_wep$day[i] & submarine$Stricken>Timeline_wep$day[i]),]$Tube)
  Timeline_wep$Torpedoes[i]=sum(submarine[(submarine$Operator=="Algeria" & submarine$Comm<=Timeline_wep$day[i] & submarine$Stricken>Timeline_wep$day[i]),]$Torpedo)
  Timeline_wep$VLS[i]=sum(submarine[(submarine$Operator=="Algeria" & submarine$Comm<=Timeline_wep$day[i] & submarine$Stricken>Timeline_wep$day[i]),]$VLS)
  Timeline_wep$SLBM[i]=sum(submarine[(submarine$Operator=="Algeria" & submarine$Comm<=Timeline_wep$day[i] & submarine$Stricken>Timeline_wep$day[i]),]$SLBM)
  Timeline_wep$Mine[i]=sum(submarine[(submarine$Operator=="Algeria" & submarine$Comm<=Timeline_wep$day[i] & submarine$Stricken>Timeline_wep$day[i]),]$mine_dedicated)
  }

Timeline_wep2=melt(Timeline_wep[,c(1:6)], id.vars=c("day"),variable.name = "Weapons")

g1=ggplot(Timeline_wep, aes(day,Service)) + geom_area(fill="darkblue", col="black") + ggtitle("Number of submarines in service") + xlab("date") + ylab("number of submarines") + theme(legend.position="bottom", axis.title.x = element_blank())
g2=ggplot(Timeline_wep2, aes(day,value)) + geom_area(aes(fill=Weapons), col="black") + scale_fill_manual(values=c(
     "Mine"="brown",
     "SLBM"="orange",
     "VLS"="forestgreen",
     "Torpedoes"="blue",
     "Torpedo_tubes"="darkblue")) + ggtitle("Weapons carried in service") + xlab("date") + ylab("number of weapons") + theme(legend.position="bottom")

print(g1/g2)
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=5}
Boat_Class_serv = data.frame(month = seq(as.Date(min(submarine$Laid)-30), as.Date(max(submarine$Stricken)+30), by="month"))
Boat_Class_serv$Construction_boat = NA
Boat_Class_serv$Service_boat = NA

for (i in 1:length(Class_list_serv)) {
  df=Boat_Class_serv
  df$Class=Class_list_serv[i]
  for (j in 1:nrow(Boat_Class_serv)) {
    df$Construction_boat[j]=sum(submarine[(submarine$Class==Class_list_serv[i] & submarine$Laid<=Boat_Class_serv$month[j] & submarine$Compl>Boat_Class_serv$month[j] & submarine$Status%in%c("new","resumed") & submarine$Operator=="Algeria"),]$value)
    df$Service_boat[j]=sum(submarine[(submarine$Class==Class_list_serv[i] & submarine$Comm<=Boat_Class_serv$month[j] & submarine$Stricken>Boat_Class_serv$month[j] & submarine$Operator=="Algeria"),]$value)
  }
  if(i==1) {
    Boat_Class_serv_tot=df
  } else if (i>1) {
    Boat_Class_serv_tot=rbind(Boat_Class_serv_tot,df)
  }
}

g15=ggplot(Boat_Class_serv_tot, aes(month,Construction_boat)) + geom_area(aes(fill=Class), col="black") + ggtitle("operated submarines under construction by Class") + xlab("date") + ylab("number of submarines") + theme(legend.position="bottom", axis.title.x = element_blank(), axis.title.y = element_blank())
g16=ggplot(Boat_Class_serv_tot, aes(month,Service_boat)) + geom_area(aes(fill=Class), col="black") + ggtitle("operated submarines in service by Class") + xlab("date") + ylab("number of submarines") + theme(legend.position="bottom", axis.title.x = element_blank(), axis.title.y = element_blank())
print((g15+g16))
```

# Individual submarines by class

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=9}
class_count_fcn=function(class) {
submarine_class=submarine[submarine$Class==class,]

Boat_Class = data.frame(month = seq(as.Date(min(submarine_class$Laid)-30), as.Date(max(submarine_class$Stricken)+30), by="month"))
Boat_Class$Construction_boat = NA
Boat_Class$Service_boat = NA

builder_list=unique(submarine_class$Builder)
operator_list=unique(submarine_class$Operator)

for (i in 1:length(builder_list)) {
  df=Boat_Class
  df$Builder=builder_list[i]
  for (j in 1:nrow(Boat_Class)) {
    df$Construction_boat[j]=sum(submarine_class[(submarine_class$Builder==builder_list[i] & submarine_class$Laid<=Boat_Class$month[j] & submarine_class$Compl>Boat_Class$month[j] & submarine_class$Status%in%c("new","resumed")),]$value)
  }
  if(i==1) {
    Boat_Class_prod=df
  } else if (i>1) {
    Boat_Class_prod=rbind(Boat_Class_prod,df)
  }
}

for (i in 1:length(operator_list)) {
  df=Boat_Class
  df$Operator=operator_list[i]
  for (j in 1:nrow(Boat_Class)) {
    df$Service_boat[j]=sum(submarine_class[(submarine_class$Operator==operator_list[i] & submarine_class$Comm<=Boat_Class$month[j] & submarine_class$Stricken>Boat_Class$month[j]),]$value)
  }
  if(i==1) {
    Boat_Class_serv=df
  } else if (i>1) {
    Boat_Class_serv=rbind(Boat_Class_serv,df)
  }
}

g13=ggplot(Boat_Class_prod, aes(month,Construction_boat)) + geom_area(aes(fill=Builder), col="black") + ggtitle("built submarine_class_classs under construction by Builder") + 
  xlab("date") + ylab("number of submarines") + theme(legend.position="bottom", axis.title.x = element_blank(), axis.title.y = element_blank())
g14=ggplot(Boat_Class_serv, aes(month,Service_boat)) + geom_area(aes(fill=Operator), col="black") + ggtitle("built submarine_class_classs in service by Builder") + 
  xlab("date") + ylab("number of submarines") + theme(legend.position="bottom", axis.title.x = element_blank(), axis.title.y = element_blank())

print(g13+g14)
}
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=9}
class_batch_fcn=function(class) {
submarine_class=submarine[submarine$Class==class,]

Boat_Class = data.frame(month = seq(as.Date(min(submarine_class$Laid)-30), as.Date(max(submarine_class$Stricken)+30), by="month"))
Boat_Class$Construction_boat = NA
Boat_Class$Service_boat = NA

batch_list=unique(submarine_class$Batch)

for (i in 1:length(batch_list)) {
  df=Boat_Class
  df$Batch=batch_list[i]
  for (j in 1:nrow(Boat_Class)) {
    df$Construction_boat[j]=sum(submarine_class[(submarine_class$Batch==batch_list[i] & submarine_class$Laid<=Boat_Class$month[j] & submarine_class$Compl>Boat_Class$month[j] & submarine_class$Status%in%c("new","resumed")),]$value)
    df$Service_boat[j]=sum(submarine_class[(submarine_class$Batch==batch_list[i] & submarine_class$Comm<=Boat_Class$month[j] & submarine_class$Stricken>Boat_Class$month[j]),]$value)
  }
  if(i==1) {
    Boat_Class_batch=df
  } else if (i>1) {
    Boat_Class_batch=rbind(Boat_Class_batch,df)
  }
}

g17=ggplot(Boat_Class_batch, aes(month,Construction_boat)) + geom_area(aes(fill=Batch), col="black") + ggtitle("built submarine_class_classs under construction by Version") +
  xlab("date") + ylab("number of submarines") + theme(legend.position="bottom", axis.title.x = element_blank(), axis.title.y = element_blank())
g18=ggplot(Boat_Class_batch, aes(month,Service_boat)) + geom_area(aes(fill=Batch), col="black") + ggtitle("built submarine_class_classs in service by Version") +
  xlab("date") + ylab("number of submarines") + theme(legend.position="bottom", axis.title.x = element_blank(), axis.title.y = element_blank())
print(g17+g18)
}
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=9}
class_serv_fcn=function(class) {
submarine_class=submarine[submarine$Class==class,]

Timeline=data.frame(day=seq(as.Date(min(submarine_class$Laid)-30), as.Date("2024-06-01"), by="month"))
Timeline$Incomplete=NA
Timeline$Retired=NA
Timeline$Ex_Captured=NA
Timeline$Captured=NA
Timeline$Ex_Transferred=NA
Timeline$Transferred=NA
Timeline$Scuttled=NA
Timeline$Lost=NA
Timeline$Reserve=NA
Timeline$Service=NA
Timeline$Transit=NA
Timeline$Construction=NA

for (i in 1:nrow(Timeline)) {
  Timeline$Construction[i]=sum(submarine_class[(submarine_class$Laid<=Timeline$day[i] & submarine_class$Compl>Timeline$day[i] & submarine_class$Status=="new"),]$value)
  Timeline$Transit[i]=sum(submarine_class[(submarine_class$Compl<=Timeline$day[i] & submarine_class$Comm>Timeline$day[i] & submarine_class$Status=="new"),]$value)
  Timeline$Service[i]=sum(submarine_class[(submarine_class$Comm<=Timeline$day[i] & submarine_class$Decomm>Timeline$day[i]),]$value)
  Timeline$Reserve[i]=sum(submarine_class[(submarine_class$Decomm<=Timeline$day[i] & submarine_class$Stricken>Timeline$day[i]),]$value)
  Timeline$Lost[i]=sum(submarine_class[(submarine_class$Stricken<=Timeline$day[i] & submarine_class$Fate%in%c("lost","total loss")),]$value)
  Timeline$Scuttled[i]=sum(submarine_class[(submarine_class$Stricken<=Timeline$day[i] & submarine_class$Fate=="scuttled"),]$value)
  Timeline$Transferred[i]=sum(submarine_class[(submarine_class$Stricken<=Timeline$day[i] & submarine_class$Foreign>Timeline$day[i] & submarine_class$Fate%in%c("transferred","transferred incomplete")),]$value)
  Timeline$Ex_Transferred[i]=sum(submarine_class[(submarine_class$Foreign<=Timeline$day[i] & submarine_class$Fate%in%c("transferred","transferred incomplete")),]$value)
  Timeline$Captured[i]=sum(submarine_class[(submarine_class$Stricken<=Timeline$day[i] & submarine_class$Foreign>Timeline$day[i] & submarine_class$Fate%in%c("captured","captured incomplete")),]$value)
  Timeline$Ex_Captured[i]=sum(submarine_class[(submarine_class$Foreign<=Timeline$day[i] & submarine_class$Fate%in%c("captured","captured incomplete")),]$value)
  Timeline$Incomplete[i]=sum(submarine_class[(submarine_class$Stricken<=Timeline$day[i] & submarine_class$Fate=="incomplete"),]$value)
  Timeline$Retired[i]=sum(submarine_class[(submarine_class$Stricken<=Timeline$day[i] & submarine_class$Fate%in%c("hulked","museum","retired","surrendered")),]$value)
}

Timeline2=melt(Timeline, id.vars=c("day"),variable.name = "Status")

g23=ggplot(Timeline2, aes(day,value)) + geom_area(aes(fill=Status), col="black") + scale_fill_manual(values=c(
     "Incomplete"="lemonchiffon",
     "Retired"="lightgrey",
     "Transferred"="forestgreen",
     "Ex_Transferred"="lightgreen",
     "Captured"="brown",
     "Ex_Captured"="lightsalmon",
     "Scuttled"="purple",
     "Lost"="red",
     "Reserve"="lightblue",
     "Service"="darkblue",
     "Transit"="lightblue",
     "Construction"="goldenrod1")) + ggtitle(paste(class)) + xlab("date") + ylab("number of submarines") + theme(legend.position="bottom", axis.title.x = element_blank(), axis.title.y = element_blank())

print(g23)
}
```

```{r, warning=F, echo=F, message=F}
class_fcn=function(class) {
print(ggplot(submarine[submarine$Class==class & submarine$Operator=="Algeria",], aes(x=as.factor(Submarine), ymin=Laid, ymax=Compl)) +
        geom_linerange(col="goldenrod1", size=6) +
        geom_linerange(aes(ymin=Compl, ymax=Comm), col="lightgreen", size=6) + 
        geom_linerange(aes(ymin=Comm, ymax=Decomm), col="royalblue", size=6) + 
        geom_linerange(aes(ymin=Decomm, ymax=Stricken), col="lightblue", size=6) + 
        geom_linerange(aes(ymin=Stricken, ymax=Sold), col="gainsboro", size=6) + 
        geom_linerange(aes(ymin=Sold, ymax=Foreign), col="lightgreen", size=6) + 
        geom_point(aes(y=Stricken, col=Fate), size=4) +
        geom_text(aes(label=paste0(Fate," ",Receiver2),y=Stricken, col=Fate), size=4,hjust=-0.05) + scale_color_manual(values=c(
          "active"="darkblue",
          "building"="goldenrod1",
          "captured"="brown",
          "captured incomplete"="brown",
          "hulked"="black",
          "incomplete"="goldenrod1",
          "lost"="red",
          "modernized"="goldenrod1",
          "museum"="black",
          "reserve"="lightblue",
          "retired"="black",
          "scuttled"="purple",
          "surrendered"="brown",
          "total loss"="red",
          "transferred"="forestgreen",
          "transferred incomplete"="forestgreen")) +
        geom_text(aes(label=Version, y=min(submarine[submarine$Class==class & submarine$Operator=="Algeria",]$Order, na.rm=T)), size=3,hjust=-0.05) +
        geom_hline(yintercept=as.Date("1914-07-01"), linetype="dashed", color = "forestgreen", size=1.5) +
        geom_hline(yintercept=as.Date("1918-11-01"), linetype="dashed", color = "forestgreen", size=1.5) +
        geom_hline(yintercept=as.Date("1939-09-01"), linetype="dashed", color = "forestgreen", size=1.5) +
        geom_hline(yintercept=as.Date("1945-09-01"), linetype="dashed", color = "forestgreen", size=1.5) +
        scale_x_discrete(limits = rev(levels(as.factor(submarine[submarine$Class==class & submarine$Operator=="Algeria",]$Submarine)))) +
        coord_flip() + xlab("date") + ylab("submarine name") + theme(legend.position="none", axis.title.x = element_blank(), axis.title.y = element_blank()))
}
```

## Specification summaries

```{r, warning=F, echo=F, message=F, fig.width=13, fig.height=4/4+1}
g1=ggplot(specs, aes(Submarines, Total)) + geom_col(col="black", aes(fill=Design), alpha=0.5) +
  geom_col(aes(x=Submarines, y=Number, fill=Design), col="black") +
  scale_x_discrete(limits = rev(levels(as.factor(specs$Submarines)))) +
  geom_text(aes(label=Total_text, x=Submarines, y=0),  hjust=-0.02) + coord_flip() + ggtitle("Number of submarines by class") + labs(x="", y="")

g2=ggplot(specs, aes(Submarines, Disp_full_sub_t)) + geom_col(col="black", fill="blue1") +
  geom_col(aes(x=Submarines, Disp_full_surf_t), col="black", fill="blue3") +
  scale_x_discrete(limits = rev(levels(as.factor(specs$Submarines)))) +
  geom_text(aes(label=paste(Disp_full_surf_t,"/",Disp_full_sub_t), x=Submarines, y=0), col="red",  hjust=-0.02) + coord_flip() + ggtitle("Displacement by class (t)") + labs(x="", y="")

(g1+g2)
```

```{r, warning=F, echo=F, message=F, fig.width=13, fig.height=4/2+2}

g3=ggplot(specs, aes(Submarines, Power_surf_HP)) + geom_col(col="black", fill="green3") +
  scale_x_discrete(limits = rev(levels(as.factor(specs$Submarines)))) +
  geom_text(aes(label=Power_surf_HP, x=Submarines, y=(0),  hjust=-0.02)) + coord_flip() + ggtitle("Surface horsepower") + labs(x="", y="")

g4=ggplot(specs, aes(Submarines, Speed_surf_kts)) + geom_col(col="black", fill="forestgreen") +
  scale_x_discrete(limits = rev(levels(as.factor(specs$Submarines)))) +
  geom_text(aes(label=Speed_surf_kts, x=Submarines, y=(0),  hjust=-0.02)) + coord_flip() + ggtitle("Surface speed (kts)") + labs(x="", y="")

g5=ggplot(specs, aes(Submarines, Power_sub_HP)) + geom_col(col="black", fill="green3") +
  scale_x_discrete(limits = rev(levels(as.factor(specs$Submarines)))) +
  geom_text(aes(label=Power_sub_HP, x=Submarines, y=(0),  hjust=-0.02)) + coord_flip() + ggtitle("Submerged horsepower") + labs(x="", y="")

g6=ggplot(specs, aes(Submarines, Speed_sub_kts)) + geom_col(col="black", fill="forestgreen") +
  scale_x_discrete(limits = rev(levels(as.factor(specs$Submarines)))) +
  geom_text(aes(label=Speed_sub_kts, x=Submarines, y=(0),  hjust=-0.02)) + coord_flip() + ggtitle("Submerged speed (kts)") + labs(x="", y="")

(g3+g4)/(g5+g6)

g7=ggplot(specs, aes(Submarines, Fuel_t)) + geom_col(col="black", fill="grey") +
  scale_x_discrete(limits = rev(levels(as.factor(specs$Submarines)))) +
  geom_text(aes(label=Fuel_t, x=Submarines, y=(0),  hjust=-0.02)) + coord_flip() + ggtitle("Fuel storage (t)") + labs(x="", y="")

g8=ggplot(specs, aes(Submarines, Range_surf_nm)) + geom_col(col="black", fill="lightblue") +
  scale_x_discrete(limits = rev(levels(as.factor(specs$Submarines)))) +
  geom_text(aes(label=Range_surf_nm, x=Submarines, y=(0),  hjust=-0.02)) + coord_flip() + ggtitle("Surface range (nm)") + labs(x="", y="")

g9=ggplot(specs, aes(Submarines, Depth_m)) + geom_col(col="black", fill="blue3") +
  scale_x_discrete(limits = rev(levels(as.factor(specs$Submarines)))) +
  geom_text(aes(label=Depth_m, x=Submarines, y=(0),  hjust=-0.02), col="red") + coord_flip() + ggtitle("Diving depth (m)") + labs(x="", y="")

g10=ggplot(specs, aes(Submarines, Range_sub_nm)) + geom_col(col="black", fill="lightblue") +
  scale_x_discrete(limits = rev(levels(as.factor(specs$Submarines)))) +
  geom_text(aes(label=Range_sub_nm, x=Submarines, y=(0),  hjust=-0.02)) + coord_flip() + ggtitle("Submerged range (nm)") + labs(x="", y="")

(g7+g8)/(g9+g10)

g11=ggplot(weaps, aes(Submarines, Torpedoes)) + geom_col(col="black", fill="blue1") +
  geom_col(aes(x=Submarines, Tubes), col="black", fill="blue3") +
  scale_x_discrete(limits = rev(levels(as.factor(weaps$Submarines)))) +
  geom_text(aes(label=Torpedo_text2, x=Submarines, y=0), col="red",  hjust=-0.02) + coord_flip() + ggtitle("Torpedo armement") + labs(x="", y="")

g12=ggplot(weaps, aes(Submarines, Mine_tot)) + geom_col(col="black", fill="brown2") +
  geom_col(aes(x=Submarines, Mines), col="black", fill="brown") +
  scale_x_discrete(limits = rev(levels(as.factor(weaps$Submarines)))) +
  geom_text(aes(label=Mine_text, x=Submarines, y=0), col="black",  hjust=-0.02) + coord_flip() + ggtitle("Mine armement") + labs(x="", y="")

g13=ggplot(weaps, aes(Submarines, VLS)) + geom_col(fill="forestgreen", col="black") +
  scale_x_discrete(limits = rev(levels(as.factor(weaps$Submarines)))) +
  geom_text(aes(label=VLS_text, x=Submarines, y=0),  hjust=-0.02) + coord_flip() + ggtitle("Vertical launch systems") + labs(x="", y="")

g14=ggplot(weaps, aes(Submarines, SLBLS)) + geom_col(fill="orange", col="black") +
  scale_x_discrete(limits = rev(levels(as.factor(weaps$Submarines)))) +
  geom_text(aes(label=SLBM_text, x=Submarines, y=0),  hjust=-0.02) + coord_flip() + ggtitle("Submarine launched ballistic missiles") + labs(x="", y="")

(g11+g12)/(g13+g14)
```

## Romeo class (Project 633)

The first Algerian submarines were second-hand Soviet Romeo class which had a short career. They were more training boats then anything else until the arrival of the new Kilo boats.

```{r, warning=F, echo=F, message=F}
kable(specs[specs$Class=="Project 633",c("Version","Boats","Number","Displacement_t","Propulsion","Power_HP","Fuel_t","Speed_kts","Range_nm","Depth_m")])
kable(weaps[weaps$Class=="Project 633",c("Version","Boats","Year","Torpedo_text")])
```

![](https://www.shipbucket.com/files/real/DZ/Project%20633%20(Romeo)/none/9235_010_20230511193114.png)

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=4}
class_serv_fcn(class="Project 633")
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=2/4+1}
class_fcn(class="Project 633")
```

## Kilo class (Projects 877 and 636)

Algeria's current submarine force consists of 3 pairs of Kilo class submarines acquired new from the Soviet Union, and then Russia over several decades.

```{r, warning=F, echo=F, message=F}
kable(specs[specs$Class=="Project 877",c("Version","Boats","Number","Displacement_t","Propulsion","Power_HP","Fuel_t","Speed_kts","Range_nm","Depth_m")])
kable(weaps[weaps$Class=="Project 877",c("Version","Boats","Year","Torpedo_text","Missile_text","Light_SAM")])
```

![](https://www.shipbucket.com/files/real/DZ/Project%20636M%20Varshavyanka%20(Improved%20Kilo)/none/9077_021MessalielHadj_20230511193118.png)

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=4}
class_serv_fcn(class="Project 877")
class_batch_fcn(class="Project 877")
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=6/4+1}
class_fcn(class="Project 877")
```

# Full summary

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=(8/4+1)}
submarine$Submarine=fct_reorder(submarine$Submarine, submarine$Rank)
ggplot(submarine[submarine$Operator=="Algeria",], aes(x=as.factor(Submarine), ymin=Laid, ymax=Compl)) +
        geom_linerange(col="goldenrod1", size=6) +
        geom_linerange(aes(ymin=Compl, ymax=Comm), col="lightgreen", size=6) + 
        geom_linerange(aes(ymin=Comm, ymax=Decomm), col="royalblue", size=6) + 
        geom_linerange(aes(ymin=Decomm, ymax=Stricken), col="lightblue", size=6) + 
        geom_linerange(aes(ymin=Stricken, ymax=Sold), col="gainsboro", size=6) + 
        geom_linerange(aes(ymin=Sold, ymax=Foreign), col="lightgreen", size=6) + 
        geom_point(aes(y=Stricken, col=Fate), size=4) +
        geom_text(aes(label=paste0(Fate," ",Receiver2),y=Stricken, col=Fate), size=3,hjust=-0.05) + scale_color_manual(values=c(
          "active"="darkblue",
          "building"="goldenrod1",
          "captured"="brown",
          "captured incomplete"="brown",
          "hulked"="black",
          "incomplete"="goldenrod1",
          "lost"="red",
          "modernized"="goldenrod1",
          "museum"="black",
          "reserve"="lightblue",
          "retired"="black",
          "scuttled"="purple",
          "surrendered"="brown",
          "total loss"="red",
          "transferred"="forestgreen",
          "transferred incomplete"="forestgreen")) +
        geom_text(aes(label=Version, y=min(submarine[submarine$Operator=="Algeria",]$Order, na.rm=T)), size=3,hjust=-0.05) +
        geom_hline(yintercept=as.Date("1914-07-01"), linetype="dashed", color = "forestgreen", size=1.5) +
        geom_hline(yintercept=as.Date("1918-11-01"), linetype="dashed", color = "forestgreen", size=1.5) +
        geom_hline(yintercept=as.Date("1939-09-01"), linetype="dashed", color = "forestgreen", size=1.5) +
        geom_hline(yintercept=as.Date("1945-09-01"), linetype="dashed", color = "forestgreen", size=1.5) +
        scale_x_discrete(limits = rev(levels(as.factor(submarine[submarine$Operator=="Algeria",]$Submarine)))) +
        coord_flip() + xlab("submarine name") + ylab("date") + theme(legend.position="none", axis.title.x = element_blank(), axis.title.y = element_blank())
```
