---
title: "Colombia"
output: html_document
date: "2025-02-25"
---

```{r, warning=F, echo=F, message=F}
source("Functions.R")
country="Colombia"
management_fcn()
```

Colombia is a South American nation of 53.2 million inhabitants with two seperate coastlines on the Pacific ocean and Caribbean sea. Colombia declared independance in 1810, and it's navy dates from 1823.

Contrary two some other South American nations, the navy was never very large and didn't operate submarines until the acquisition of a pair of type 209 submarines in the 1970s, along some midget submarines. These were complemented by four ex-German navy Type 206As in 2012. All four are in service today.

# Submarines operated by Colombia

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=5}
summary_fcn()
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=7}
weapons_fcn()
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=5}
class_fcn()
```

# Individual submarines by class

## Specification summaries

```{r, warning=F, echo=F, message=F, fig.width=15, fig.height=2/4+1}
specs1_fcn()
```

```{r, warning=F, echo=F, message=F, fig.width=15, fig.height=2/2+2}
specs2_fcn()
```

## Type 209

Two Type 209/1200 boats

```{r, warning=F, echo=F, message=F}
kable(specs[specs$Class=="Type 209",c("Version","Boats","Number","Displacement","Propulsion","Power","Fuel","Speed","Range","Depth")])
kable(weaps[weaps$Class=="Type 209",c("Version","Boats","Year","Torpedo_text")])
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=4}
class_serv_fcn(class="Type 209")
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=2/4+1}
class_sub_fcn(class="Type 209")
```

## Type 206

Ex-German navy boats

```{r, warning=F, echo=F, message=F}
kable(specs[specs$Class=="Type 206",c("Version","Boats","Number","Displacement","Propulsion","Power","Fuel","Speed","Range","Depth")])
kable(weaps[weaps$Class=="Type 206",c("Version","Boats","Year","Torpedo_text","Mines")])
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=4}
class_serv_fcn(class="Type 206")
```

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=2/4+1}
class_sub_fcn(class="Type 206")
```

# Full summary

```{r, warning=F, echo=F, message=F, fig.width=10, fig.height=(4/4+1)}
individual_fcn()
```
